%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional  Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}


%---------------------------------------------------------
  \cventrynew
    {Senior System Developer | \textnormal{\textit{HEO | Foreign, Commonwealth and Development Office, UK.}}} % Job title
    {June 2019 - December 2023} % Date (s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led software and infrastructure development for the UK aid tracker, resulting in an 80\% increase in application efficiency.}
        %\item {Oversee application operations, manage team, design software development and deployment strategy.}
        \item {Designed and managed {\bf CI/CD} workflows for application deployment, reducing the release cycle by 40\%.}
        \item {Implemented {\bf OWASP} secure coding practices, reducing security vulnerabilities by 25\%.}   
        %\item {Perform data analysis, generate aid transparency reports and publish on public domain.}
        \item {Conducted data analysis and published transparency data in the public domain.}
        \item {Automated data publication process by integrating {\bf EDRM} with transparency data publisher, reducing human interaction by 90\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
 {System Developer | \textnormal {\textit{Foreign, Commonwealth and Development Office, UK.}}} % Job title
    {March 2013 - May 2019} % Date (s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed project specifications, ensuring optimal code performance.} 
        \item {Executed unit tests, debugged code, and consistently maintained to uphold code quality and compliance with standards.}
        \item {Developed and integrated {\bf WebAPI}’s, maintaining accessibility standards.}
        \item {Spearheaded application operations, devised agile dev strategy, and improved documentation for peak performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    % {} % Organisation
    {Executive IT | \textnormal{\textit{Pacific Bangladesh Telecom Limited}, Bangladesh.}} % Job title
    % % {Bombay, India} % Location
    {June 2012 - March 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented automation initiatives, increasing operational efficiency by 25\%.}
        \item {Collaborated in cross-functional activities, including application development and data analysis.}
        %\item {Designed and developed a cash management solution using {\bf Asp.Net} and {\bf MSSQL}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    {Executive IT | \textnormal{\textit{Uttara Group of Companies Limited}, Bangladesh.}} % Organisation
    % {} % Job title % Job title
    % {TamilNadu, India} % Location
    {December 2010 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Spearheaded the development and maintenance of in-house software dedicated to supporting {\bf OSS} and retail business operations.} 
        \item {Programmed a comprehensive {\bf enterprise resource planning} system using the {\bf .NET} framework and {\bf MSSQL} database.}
        \item {Designed and developed a real-time inventory management system, reducing manual tasks by 90\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries2}
