%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


%----------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {UK government's core business solution for aid distribution and tracking.} % Organisation
    {Aid Management Platform} % Project
    {January 2016 - December 2023} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
       \item {ASP.NET Core, JavaScript, Angular, CQRS design pattern, MSSQL, Web API, GitHub, Azure DevOps.}    
      \end{cvitems}
    }
    

%---------------------------------------------------------
  \cventry
    {Integrated business processes, consolidating functions for enhanced efficiency and decision-making.} % Project
    {ERP Solution} % Organisation
    {December 2010 - May 2012} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
       \item{C\#, ASP.Net, JavaScript, JQuery, MSSQL, Remote server integration.}
      \end{cvitems}
    }


  \cventry
    {Developed an inventory management system with all management reports.} % Organisation
    {Inventory Management System of Vehicle Parts} % Project
    { December 2010 - June 2012} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
        \item {ASP.Net, JavaScript, Ajax, HTML, CSS, MSSQL, IIS}        
      \end{cvitems}
    }
    

  \cventry
    {Streamlined procurement processes, tracking, management, and optimization of purchases.} % Organisation
    {Purchase Order Solution } % Project
    {October 2013 - May 2014} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
        \item {ASP.NET, MSSQL, JavaScript, JQuery, bootstrap, IIS, SSRS, Crystal Report.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Implemented ETL solutions for the billing department.} % Organisation
    {ETL System for Pacific Bangladesh Telecom Ltd.} % Project
    {July 2012 - March 2013} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
        \item {MSSQL, SSIS, SSAS, SSRS, IIS, WebUI, Crystal Report.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
